\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-01-12 sections/results.tex
Add: TODOs to results section

@@

>>>>

  % TODO: This is the most important statement (look at the dada2 paper for better arguments)
  We prefer dada2 because it peforms marginally better (value??) than the other methods and it is also performs independent of the taxonomy database (so does denovo why are you suggesting this then?).
  Denovo also performs better but the denoising helps when there are more sequences (where is the proof?) [ref]

@@

 % TODO: This is the most important statement here
 From previous studies, (refer to the Bokulich2018 paper here) which have done more quantitative benchmarks on the subject of which tool is the best (for classifer)...
 There are also other studies, [ref] that focus on the database aspect and they too have found that...
